Analysis 3

### 2023-11-17 Lahman Analysis/Rough Analysis 2/Analysis3.qmd
Add 3aa model and update 3b model
The 3b still does not work, apparently because the initial conditions (random between -2 and 2) are too extreme for the quartic design. We could fix that by setting initial conditions or by using orthogonal polynomials in place of a raw quartic.

@@

```{r}
data3b <- list(
  N = nrow(Samp_Batting),
  n_player = n_distinct(Samp_Batting$player_index),
  AB = Samp_Batting %>% pull(AB),
  HR = Samp_Batting %>% pull(HR),
  Player = Samp_Batting %>% pull(player_index),
  cAge = Samp_Batting %>% pull(Age) -30,
  cAgeSq = (Samp_Batting %>% pull(Age) -30)**2,
  cAgeCb = (Samp_Batting %>% pull(Age) -30)**3,
  cAgeQa = (Samp_Batting %>% pull(Age) -30)**4,
  Park = Samp_Batting %>% pull(park_index)
)
```

>>>>

## Adjust 3a model

In the 11/17 meeting, we changed how parks entered the model.

```{r}
data3aa <- list(
  N = nrow(Samp_Batting),
  n_player = n_distinct(Samp_Batting$player_index),
  n_park = n_distinct(Samp_Batting$park_index),
  AB = Samp_Batting %>% pull(AB),
  HR = Samp_Batting %>% pull(HR),
  Player = Samp_Batting %>% pull(player_index),
  cAge = Samp_Batting %>% pull(Age) -30,
  cAgeSq = (Samp_Batting %>% pull(Age) -30)**2,
  Park = Samp_Batting %>% pull(park_index)
)
```

```{r}
fit3aa <- stan(
  file = "HR3aa.stan",
  data = data3aa,
  iter = 2000
)
```

```{r}
print(fit3aa, pars = c("mu5", "sigma5"))
```

@@

```{r}
data3b <- list(
  N = nrow(Samp_Batting),
  n_player = n_distinct(Samp_Batting$player_index),
  n_park = n_distinct(Samp_Batting$park_index),
  AB = Samp_Batting %>% pull(AB),
  HR = Samp_Batting %>% pull(HR),
  Player = Samp_Batting %>% pull(player_index),
  cAge = Samp_Batting %>% pull(Age) -30,
  cAgeSq = (Samp_Batting %>% pull(Age) -30)**2,
  cAgeCb = (Samp_Batting %>% pull(Age) -30)**3,
  cAgeQa = (Samp_Batting %>% pull(Age) -30)**4,
  Park = Samp_Batting %>% pull(park_index)
)
```
